---
title: "Predictive model for StarWars data"
output: 
  html_document:
    toc: true
---

# Read data

Read the data from the kaggle website https://www.kaggle.com/jsphyg/star-wars#characters.csv.

```{r warning=FALSE, message=FALSE}
library("openxlsx")
library("missRanger")
library("randomForest")
charactersStarWars <- read.xlsx("charactersStarWars.xlsx")
```

# Data Preprocessing

Change characters into factors.

```{r warning=FALSE, message=FALSE}
set.seed(1)

rownames(charactersStarWars) <- charactersStarWars[,1]
charactersStarWars <- charactersStarWars[,c(2,3,4,5,6,8,9,10,11)]
charactersStarWars$hair_color <- factor(gsub(charactersStarWars$hair_color, pattern = ",.*", replacement = ""))
charactersStarWars$skin_color <- factor(gsub(charactersStarWars$skin_color, pattern = ",.*", replacement = ""))
charactersStarWars$gender <- factor(charactersStarWars$gender)
charactersStarWars$eye_color <- factor(gsub(charactersStarWars$eye_color, pattern = "[,-].*", replacement = ""))
charactersStarWars$homeworld <- factor(charactersStarWars$homeworld)
charactersStarWars$species <- factor(charactersStarWars$species)

charactersStarWarsFilled <- missRanger(charactersStarWars)

head(charactersStarWarsFilled)
```


# Create a gbm model

Let's use `gbm` library to create a `gbm` model with 250 trees 3 levels deep.

```{r warning=FALSE, message=FALSE}
library("gbm")
set.seed(1)

model <- gbm(Jedi~height + mass + hair_color + skin_color + eye_color + gender , data = charactersStarWarsFilled)
```

# Create a DALEX explainer

Let's wrap gbm model into a DALEX explainer.

```{r warning=FALSE, message=FALSE}
library("DALEX")
model_explained <- explain(model, charactersStarWarsFilled, y = charactersStarWarsFilled$Jedi)
```

# Feature Importance explainer

Calculate Feature Importnace explainer.

```{r warning=FALSE, message=FALSE}
library("ingredients")
library("auditor")
plot(feature_importance(model_explained, loss_function = DALEX:::loss_one_minus_auc))

plot_roc(model_evaluation(model_explained))
```


# modelStudio app

Calculate modelStudio dashboard.

```{r eval = FALSE}
library(modelStudio)
op <- modelStudioOptions(
  subtitle = "What makes a Jedi (or Sith)?"
)
modelStudioStarWars <- modelStudio(mexp, 
                  new_observation = charactersFilled[,1:6],
                  options = op)
modelStudioStarWars

r2d3::save_d3_html(modelStudioStarWars, file = "index.html")
```

